### 2016-06-07 paper/fig_runtimes-table.tex
added some latex bug fixes

\csvreader[tabular=|l|l|,
    table head=\hline\textbf{Test} & \textbf{Example Count} \\\hline,
    late after line = \\\hline]%
{generated-data/data.csv}{Test=\Test,ExamplesRequired=\ExamplesRequired}%
{\Test{} & \ExamplesRequired{}}%

%\hline\textbf{Test} & \textbf{Examples Required}
%\\\hline\hline
%\csvreader[head to column names]{generated-data/data.csv}{}
%{\Test& \ExamplesRequired\\\hline}
%\end{tabular}
\caption{Examples Required Table}
\label{fig:examples-required-table}
\end{figure}

>>>>

\csvreader[tabular=|l|l|,
    table head=\hline\textbf{Test} & \textbf{Time (s)} \\\hline,
    late after line = \\\hline]
{generated-data/data.csv}{Test=\Test,ComputationTime=\ComputationTime}
{\Test{} & \ComputationTime{}}

%\hline\textbf{Test} & \textbf{Examples Required}
%\\\hline\hline
%\csvreader[head to column names]{generated-data/data.csv}{}
%{\Test& \ExamplesRequired\\\hline}
%\end{tabular}
\caption{Runtime Table}
\label{fig:runtimes-table}
\end{figure}
